The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-03-14 mnras_guide.tex
update

\section{Methodology}
\label{Methodology}
  We used the GPU-accelerated special relativistic\
  hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
  National Taiwan University\
  (Schive et al. \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
  to carry out the simulations of the Galactic bubbles by CR and relativistic fluid injections from the GC.

@@

  The set of \Cref{governing-eq} is closed by using the Taub-Mathews equation of state \citep{Taub,TM_EOS}\
  that approximates the exact EoS \citep{Synge} for ultra-relativistically\
  hot gases coexisting with non-relativistically cold gases.

@@

  The density profile of \Cref{disc-atm-sys} is shown in Fig. \ref{fig__initial-density-profile}.\
  Beyond the core radius ($\sim 2 \text{ kpc}$) the gaseous density decreases rapidly as a power-law.

@@

\begin{table*}[t]
\raggedright
\caption{Parameters of the disc, atmosphere, and gravitational potential in the simulations.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                             & Description                    & Value                                &  Reference                     \\ \midrule
{\bf Static stellar potential }       &                                &                                      &                                \\
$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge   & 100 km$\cdot$s$^{-1}$                & \citep{velocity-dispersion-MW} \\
$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge  & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &   N/A                          \\ \hline
{\bf Static dark halo potential }     &                                &                                      &                                \\
$v_{\text{halo}}$                     & Characteristic velocity        & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
$d_{\text{h}}$                        & Core radius                    & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
{\bf Atmosphere }                     &                                &                                      &                                \\
$T_{\text{\text{atmp}}}$              & Temperature of atmosphere      & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
{\bf Isothermal disc }                &                                &                                      &                                \\
$z_{0}$                               & Scale height of disc           & 100 pc                               & \citep{peak-ism-density}       \\
$T_{\text{\text{isoDisk}}}$           & Temperature of disc            & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disc      & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
{\bf Clumpy disc }                    &                                &                                      &                                \\
$\dagger$  $k_{\text{min}}$           & Cutoff wave number             & 375.0                                & \citep{peak-ism-density}       \\
$\mu$                                 & Mean of scalar field           & 1.0                                  &   N/A                          \\
$\ddag$  $\sigma$                     & Dispersion of scalar field     & 5.0                                  & \citep{Federrath2010}          \\
$\beta$                               & Power law index                & -5/3                                 &   N/A                          \\ \midrule
\end{tabular}
\begin{tablenotes}
      \raggedright
      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual molecular cloud $\sim 100$ pc.
      \item  $\ddag$ In numerical simulations of turbulence,\
             \citet{Federrath2010} find $\sigma\sim 3.6$ and 35 for solenoidal (divergence-free)\
             and compressive (curl-free) driving force,\
             respectively, so that our adopted value of 5 is closer to their solenoidal result.
    \end{tablenotes}
\end{table*}

@@

 The temperature profile (left middle panel in Fig. \ref{fig__profile}) along the positive z-axis in\
 Fig. \ref{fig__jetI5+ismSeed3-45deg} indicates that\
 the smooth region (purple band in Fig. \ref{fig__profile}) emitting X-ray\
 is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.

@@

 %To explore how the disk affects the formation of the Galactic bubbles,\
 We compare the clumpy disk (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
 with the smooth disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-b}),\
 specified by the initial density profile shown in Fig. \ref{fig__initial-density-profile},\
 in a stratified atmosphere.\
 The results show that the initial density distribution of\
 the dense disc has an insignificant effect\
 on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
 in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is spherical-shape,\
 suggesting the stratification facilitates the outermost bubbles elongation significantly.\
 Also, Fig. \ref{fig__jetI5+ismSeed3-45deg-c,fig__jetI5+ismSeed3-45deg-d}\
 reveal that the development of the innermost bubbles\
 is always associated with the disc, without the disc,\
 the outermost bubbles and the turbulent plasma will be oblique,\
 indicating the dense disc is crucial for\
 the symmetry of the Galactic bubbles and for the innermost bubbles formation.

 \begin{figure}%
      \captionsetup[subfigure]{labelformat=simple}
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-a}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-a}%
      \end{subfigure}%
      \hspace{10pt}%
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-b}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-b}%
      \end{subfigure}%
      \hspace{-2pt}%
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-c}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-c}%
      \end{subfigure}%
      \hspace{-2pt}%
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-d}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-d}%
     \end{subfigure}%
      \caption{
             The slices of pressure (top), temperature (middle), and number density (bottom)\
             at the end of simulation $t=12.39$ Myr.\
             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
             for a duration $t=0$--$1.2$ Myr.\
             Comparison between the clumpy (column a)\
             and the smooth disc (column b) in a stratified atmosphere\
             shows that the initial density distribution of the dense disc has an insignificant effect\
             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
             in an uniform atmosphere (column c) is spherical-shape,\
             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
             Also, the two rightmost columns reveal that the development of the innermost bubbles\
             is always associated with the disc, without the disc (column d),\
             the outermost bubbles and the turbulent plasma will be oblique,
             indicating the dense disc is crucial for\
             the symmetry of the Galactic bubbles and for the innermost bubbles formation.
      }
      \label{fig__jetI5+ismSeed3-45deg}
 \end{figure}%

 \begin{figure}%
      \begin{subfigure}[t]{0.5\linewidth}%
         \includegraphics[height=8cm]{figures/fig__profile-1.png}%
         \label{fig__profile-1}%
      \end{subfigure}%
      \hspace{4pt}
      \begin{subfigure}[t]{0.5\linewidth}%
         \includegraphics[height=8cm]{figures/fig__profile-2.png}%
         \label{fig__profile-2}%
      \end{subfigure}%
      \caption{
             Left: the profiles of pressure (top), temperature (middle),\
             and number density (bottom)\
             along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
             Right: the close-up view of the profiles in the yellow band.\
             The sharp pressure jump at $z=3.62$ kpc\
             indicates that the innermost bubbles\
             (dashed box in the top panel in \Cref{fig__jetI5+ismSeed3-45deg-a})\
             are an expanding reverse shock.
      }%
      \label{fig__profile}%
 \end{figure}%

@@

  First, we observe that\
  The simulated eROSITA bubbles are not as limb-brightened as the observation.\
  A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
  in which CRs could increase the compressibility of the fluid,\
  resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
  The broad agreement between simulated and observed X-ray maps hints that\
  the full vertical extent of the eROSITA bubbles can be properly formed by an oblique jet within a thin disk\
  of dense ISM.

  Second, as shown in Fig. \ref{fig__jetI5+ismSeed3-45deg},\
  the half-width of the outermost bubbles is around 7 kpc,\
  corresponding to an half angular width $\sin^{-1}(7 \text{ kpc}/R_{\odot})\sim122^{\circ}$,\
  which is as wide as the eROSITA bubbles in the simulated X-ray map\
  (top panel in Fig. \ref{fig__xray_0.8keV_angle_000}).\
  We therefore suggest that the eROSITA bubble shells are a signature of compressed forward shocks\
  that have been driven into the northern and the southern Galactic halo,
  as previously proposed by \citet{Predehl2020}.

@@

We perform the double integration in \Cref{gammaray-emissivity} on each cell\
over the range of CRe Lorentz factor, and\
the range of incident photon energy between\
$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (cosmic microwave background) and\
$\epsilon_{\text{max}}=13.59$ eV (optical starlight)\
to obtain the simulated IC emissivities.

@@

where $\Gamma$ is the gamma function, $B$ is the magnetic field strength defined in\
\Cref{magnetic-field}.

@@

Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400--500 GeV,\
remarkably consistent with the observed cutoff energy.\
This is expected since\
the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) mainly arise from\
the scatterings between the relativistic CRe ($\gtrapprox 408$ GeV)\
and optical starlight ($\epsilon \sim 10$ eV).\
Thus, \Cref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
in the Klein--Nishina limit\
$\left(\text{i.e. }\epsilon_{1}\epsilon \gg \left(m_{\text{e}}c^2\right)^2\right)$,\
implying most of the CRe energy is carried away by the upscattered photons.

@@

 Finally, the comparison between\
 Fig. \ref{fig__jetI5+ismSeed3-45deg}\
 and\
 Fig. \ref{fig__jetI5+ismSeed3-45deg-CR}\
 shows that the CR pressure\
 is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
 bringing the pressure ratio of CR to gas is 0.1--0.2,
 similar to 0.18 at the beginning of the simulation.
 We therefore stress that\
 ignoring the contribution of CR pressure gradient to the momentum of the gas\
 in \Cref{governing-eq} is reasonable.

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg-CR.png}
    \caption{
     The CR pressure slice passing through the jet source at 12.39 Myr.\
     Comparison between\
     gas pressure (Fig. \ref{fig__jetI5+ismSeed3-45deg}) and cosmic ray pressure\
     shows that
     the CR pressure\
     is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
     bringing the pressure ratio of CR to gas is 0.1--0.2,
     similar to 0.18 at the beginning of the simulation.
     We therefore stress that\
     ignoring the contribution of CR pressure gradient to the momentum of the gas\
     in \Cref{governing-eq} is reasonable.
     }
    \label{fig__jetI5+ismSeed3-45deg-CR}
  \end{figure}

>>>>

\section{Methodology}
\label{Methodology}
  We used the GPU-accelerated special relativistic\
  hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
  National Taiwan University\
  (\citeauthor{gamer-1} \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
  to carry out the simulations of the Galactic bubbles by CR and relativistic fluid injections from the GC.

@@

  The set of Eq. \ref{governing-eq} is closed by using the Taub-Mathews equation of state \citep{Taub,TM_EOS}\
  that approximates the exact EoS \citep{Synge} for ultra-relativistically\
  hot gases coexisting with non-relativistically cold gases.

@@

  The density profile of Eq. \ref{disc-atm-sys} is shown in Fig. \ref{fig__initial-density-profile}.\
  Beyond the core radius ($\sim 2 \text{ kpc}$) the gaseous density decreases rapidly as a power-law.

@@

\begin{table*}
\raggedright
\caption{Parameters of the disc, atmosphere, and gravitational potential in the simulations.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                             & Description                    & Value                                &  Reference                     \\ \midrule
{\bf Static stellar potential }       &                                &                                      &                                \\
$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge   & 100 km$\cdot$s$^{-1}$                & \citep{velocity-dispersion-MW} \\
$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge  & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &   N/A                          \\ \hline
{\bf Static dark halo potential }     &                                &                                      &                                \\
$v_{\text{halo}}$                     & Characteristic velocity        & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
$d_{\text{h}}$                        & Core radius                    & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
{\bf Atmosphere }                     &                                &                                      &                                \\
$T_{\text{\text{atmp}}}$              & Temperature of atmosphere      & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
{\bf Isothermal disc }                &                                &                                      &                                \\
$z_{0}$                               & Scale height of disc           & 100 pc                               & \citep{peak-ism-density}       \\
$T_{\text{\text{isoDisk}}}$           & Temperature of disc            & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disc      & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
{\bf Clumpy disc }                    &                                &                                      &                                \\
$\dagger$  $k_{\text{min}}$           & Cutoff wave number             & 375.0                                & \citep{peak-ism-density}       \\
$\mu$                                 & Mean of scalar field           & 1.0                                  &   N/A                          \\
$\ddag$  $\sigma$                     & Dispersion of scalar field     & 5.0                                  & \citep{Federrath2010}          \\
$\beta$                               & Power law index                & -5/3                                 &   N/A                          \\ \midrule
\end{tabular}
\begin{tablenotes}
      \raggedright
      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual molecular cloud $\sim 100$ pc.
      \item  $\ddag$ In numerical simulations of turbulence,\
             \citet{Federrath2010} find $\sigma\sim 3.6$ and 35 for solenoidal (divergence-free)\
             and compressive (curl-free) driving force,\
             respectively, so that our adopted value of 5 is closer to their solenoidal result.
    \end{tablenotes}
\end{table*}

@@

 The temperature profile (left middle panel in Fig. \ref{fig__profile}) along the positive z-axis in\
 Fig. \ref{fig__jetI5+ismSeed3-45deg} indicates that\
 the temperature of the smooth region (purple band in Fig. \ref{fig__profile}) emitting X-ray\
 is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.

@@

 %To explore how the disk affects the formation of the Galactic bubbles,\
 We compare the clumpy disk (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
 with the smooth disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-b}),\
 specified by the initial density profile shown in Fig. \ref{fig__initial-density-profile},\
 in a stratified atmosphere.\
 The results show that the initial density distribution of\
 the dense disc has an insignificant effect\
 on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
 in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is spherical-shape,\
 suggesting the stratification facilitates the outermost bubbles elongation significantly.\
 Also, Fig. \ref{fig__jetI5+ismSeed3-45deg-c} and \ref{fig__jetI5+ismSeed3-45deg-d}\
 reveal that the development of the innermost bubbles\
 is always associated with the disc, without the disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-d}),\
 the outermost bubbles and the turbulent plasma will be oblique,\
 indicating the dense disc is crucial for\
 the symmetry of the Galactic bubbles and for the innermost bubbles formation.

 \begin{figure}%
      \captionsetup[subfigure]{labelformat=simple}
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-a}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-a}%
      \end{subfigure}%
      \hspace{10pt}%
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-b}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-b}%
      \end{subfigure}%
      \hspace{-2pt}%
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-c}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-c}%
      \end{subfigure}%
      \hspace{-2pt}%
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-d}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-d}%
     \end{subfigure}%
      \caption{
             The slices of pressure (top), temperature (middle), and number density (bottom)\
             at the end of simulation $t=12.39$ Myr.\
             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
             for a duration $t=0$--$1.2$ Myr.\
             Comparison between the clumpy (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
             and the smooth disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-b}) in a stratified atmosphere\
             shows that the initial density distribution of the dense disc has an insignificant effect\
             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
             in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is spherical-shape,\
             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
             Also, Fig. \ref{fig__jetI5+ismSeed3-45deg-c} and \ref{fig__jetI5+ismSeed3-45deg-d}\
             reveal that the development of the innermost bubbles\
             is always associated with the disc, without the disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-d}),\
             the outermost bubbles and the turbulent plasma will be oblique,
             indicating the dense disc is crucial for\
             the symmetry of the Galactic bubbles and for the innermost bubbles formation.
      }
      \label{fig__jetI5+ismSeed3-45deg}
 \end{figure}%

 \begin{figure}%
      \begin{subfigure}[t]{0.5\linewidth}%
         \includegraphics[height=8cm]{figures/fig__profile-1.png}%
         \label{fig__profile-1}%
      \end{subfigure}%
      \hspace{4pt}
      \begin{subfigure}[t]{0.5\linewidth}%
         \includegraphics[height=8cm]{figures/fig__profile-2.png}%
         \label{fig__profile-2}%
      \end{subfigure}%
      \caption{
             Left: the profiles of pressure (top), temperature (middle),\
             and number density (bottom)\
             along the positive z-axis in Fig. \ref{fig__jetI5+ismSeed3-45deg}.
             Right: the close-up view of the profiles in the yellow band.\
             The sharp pressure jump at $z=3.62$ kpc\
             indicates that the innermost bubbles\
             (dashed box in the top panel in Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
             are an expanding reverse shock.
      }%
      \label{fig__profile}%
 \end{figure}%

@@

  First, we observe that\
  the simulated eROSITA bubbles are not as limb-brightened as the observation.\
  A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
  in which CRs could increase the compressibility of the fluid,\
  resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
  The broad agreement between simulated and observed X-ray maps hints that\
  the full vertical extent of the eROSITA bubbles can be properly formed by an oblique jet within a thin disk\
  of dense ISM.

  Second, as shown in Fig. \ref{fig__jetI5+ismSeed3-45deg-a},\
  the half-width of the outermost bubbles is around 7 kpc,\
  corresponding to an half angular width $\sin^{-1}(7 \text{ kpc}/R_{\odot})\sim122^{\circ}$,\
  which is as wide as the eROSITA bubbles in the simulated X-ray map\
  (top panel in Fig. \ref{fig__xray_0.8keV_angle_000}).\
  We therefore suggest that the eROSITA bubble shells are a signature of compressed forward shocks\
  that have been driven into the northern and the southern Galactic halo,
  as previously proposed by \citet{Predehl2020}.

@@

We perform the double integration in Eq. \ref{gammaray-emissivity} on each cell\
over the range of CRe Lorentz factor, and\
the range of incident photon energy between\
$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (cosmic microwave background) and\
$\epsilon_{\text{max}}=13.59$ eV (optical starlight)\
to obtain the simulated IC emissivities.

@@

where $\Gamma$ is the gamma function, $B$ is the magnetic field strength defined in\
Eq. \ref{magnetic-field}.

@@

Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400--500 GeV,\
remarkably consistent with the observed cutoff energy.\
This is expected since\
the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) mainly arise from\
the scatterings between the relativistic CRe ($\gtrapprox 408$ GeV)\
and optical starlight ($\epsilon \sim 10$ eV).\
Thus, Eq. \ref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
in the Klein--Nishina limit\
$\left(\text{i.e. }\epsilon_{1}\epsilon \gg \left(m_{\text{e}}c^2\right)^2\right)$,\
implying most of the CRe energy is carried away by the upscattered photons.

@@

 Finally, the comparison between\
 Fig. \ref{fig__jetI5+ismSeed3-45deg}\
 and\
 Fig. \ref{fig__jetI5+ismSeed3-45deg-CR}\
 shows that the CR pressure\
 is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
 bringing the pressure ratio of CR to gas is 0.1--0.2,
 similar to 0.18 at the beginning of the simulation.
 We therefore stress that\
 ignoring the contribution of CR pressure gradient to the momentum of the gas\
 in Eq. \ref{governing-eq} is reasonable.

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg-CR.png}
    \caption{
     The CR pressure slice passing through the jet source at 12.39 Myr.\
     Comparison between\
     gas pressure (Fig. \ref{fig__jetI5+ismSeed3-45deg}) and cosmic ray pressure\
     shows that
     the CR pressure\
     is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
     bringing the pressure ratio of CR to gas is 0.1--0.2,
     similar to 0.18 at the beginning of the simulation.
     We therefore stress that\
     ignoring the contribution of CR pressure gradient to the momentum of the gas\
     in Eq. \ref{governing-eq} is reasonable.
     }
    \label{fig__jetI5+ismSeed3-45deg-CR}
  \end{figure}
